Title here \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2022-12-15 manuscript/manuscript.tex
removed legacy comments

\hypertarget{paragraph-headings}{%
\paragraph{System~\eqref{eq:may77} as a simple fishery model.}\label{p:may as fishery}}
We reinterpret the model~\eqref{eq:may77} as a simplified model for a fishery.
There is some precedent for this already in~\cite{may77}, however our approach here is not in 1-to-1 correspondence to the approach used in that reference.
\fm{Refers to the fact that in the reference $F(\darg)$ is our harvest quota, using constant effort.
But here, it is a predation term, we compete with the predator in this case.}

>>>>

\hypertarget{paragraph-headings}{%
\paragraph{System~\eqref{eq:may77} as a simple fishery model.}\label{p:may as fishery}}
We now reinterpret the model~\eqref{eq:may77} as a simplified model for a fishery.
The population $V$ is taken to be the a fish species which we are interested in harvesting and $H$ is some predator which feeds on $V$.

 Already~\cite{may77} has used~\eqref{eq:may77} to describe a fishery.
 However, our approach here is not in 1-to-1 correspondence to the approach used in that reference.
\footnote{
  In~\cite{may77}, the term $F(V,\ H\div \beta,\ V_0)$ is reinterpreted as a constant-effort harvest quota by humans, where $H$ is the effort expended, while the natural dynamics of $V$ is logistic growth.
  The non-linearity of the $V$-dependence on the harvest quota is justified in the fact that, for very low populations, the necessary effort to obtain a constant-size catch scales faster than $H\sim 1/V$.

  In contrast, as will be discussed in the following, our approach assumes that $V$ is predated on by some population $H$.
}
